Classless Java: Tuning Java Interfaces

### 2015-12-07 paper/sections/Translation.tex
small fix

Informally, the theorems mean that for a client program that
typechecks before a translation is applied, if the annotated type has
no subtypes, and no objects of that type are created, then type safety
is guaranteed after the successful translation. Conversely, the second
step of \mixin, namely what $\weakAnn$ does in the formalization, is
guaranteed to be type-safe for the three kinds of coherence.  \mixin
tuning is more interesting: Since \mixin does not guarantee heir
coherence, we exclude explicitly the presence of heirs. In this way
\mixin tuning guarantees only self and client coherence. The formal
theorem proofs are available in the supplementary materials.%~\ref{subsec:lemma1},~\ref{subsec:lemma2} and~\ref{subsec:theorem}.\\

>>>>

Informally, the theorems mean that for a client program that
typechecks before a translation is applied, if the annotated type has
no subtypes, and no objects of that type are created, then type safety
is guaranteed after the successful translation.

The second
step of \mixin, namely what $\weakAnn$ does in the formalization, is
guaranteed to be type-safe for the three kinds of coherence by the $\weakAnn$  tuning theorem.  
\mixin
tuning is more interesting: Since \mixin does not guarantee heir
coherence, we exclude explicitly the presence of heirs. In this way
\mixin tuning guarantees only self and client coherence. The formal
theorem proofs are available in the supplementary materials.%~\ref{subsec:lemma1},~\ref{subsec:lemma2} and~\ref{subsec:theorem}.\\
